### 2014-07-22 MS.tex
latex ms ready

6. Nieukerken EJ van, Kaila L, Kitching IJ, Kristensen NP, Lees DC, et
al. (2011) Order Lepidoptera. In:. Animal biodiversity: an outline of
higher-level classification and survey of taxonomic richness. Zootaxa.
pp. 212--221.

@@

12. Ferrer-Paris JR, S\'anchez-Mercado A, Viloria \'AL, Donaldson J (2013)
Congruence and Diversity of Butterfly-Host Plant Associations at Higher
Taxonomic Levels. PloS one 8: e63570.
doi:\href{http://dx.doi.org/0.1371/journal.pone.0063570}{0.1371/journal.pone.0063570}.

@@

19. Kodandaramaiah U, Lees DC, Müller CJ, Torres E, Karanth KP, et al.
(2010) Phylogenetics and biogeography of a spectacular Old World
radiation of butterflies: the subtribe Mycalesina (Lepidoptera:
Nymphalidae: Satyrini). BMC Evol Biol 10: 172. Available:
\url{http://www.pubmedcentral.nih.gov/articlerender.fcgi?artid=2898688\&tool=pmcentrez\&rendertype=abstract}.

20. Kodandaramaiah U, Pe\~na C, Braby MF, Grund R, Müller CJ, et al.
(2010) Phylogenetics of Coenonymphina (Nymphalidae: Satyrinae) and the
problem of rooting rapid radiations. Mol Phylogenet Evol 54: 386--394.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2009.08.012}{10.1016/j.ympev.2009.08.012}.

21. Ortiz-Acevedo E, Willmott KR (2013) Molecular systematics of the
butterfly tribe Preponini (Nymphalidae: Charaxinae). Syst Entomol:
no--o.
doi:\href{http://dx.doi.org/10.1111/syen.12008}{10.1111/syen.12008}.

22. De-Silva DL, Day JJ, Elias M, Willmott KR, Whinnett A, et al. (2010)
Molecular phylogenetics of the Neotropical butterfly subtribe Oleriina
(Nymphalidae: Danainae: Ithomiini). Mol Phylogenet Evol 55: 1032--1041.
doi:\href{http://dx.doi.org/http://dx.doi.org/10.1016/j.ympev.2010.01.010}{http://dx.doi.org/10.1016/j.ympev.2010.01.010}.

@@

44. FitzJohn RG, Maddison WP, Otto SP (2009) Estimating trait-dependent
speciation and extinction rates from incompletely resolved phylogenies.
Syst Biol 58: 595--611. Available:
\url{http://www.ncbi.nlm.nih.gov/pubmed/20525612}.

@@

52. Müller CJ, Wahlberg N, Beheregaray LB (2010) `After Africa': the
evolutionary history and systematics of the genus Charaxes Ochsenheimer
(Lepidoptera: Nymphalidae) in the Indo-Pacific region. Biol J Linn Soc
100: 457--481.
doi:\href{http://dx.doi.org/10.1111/j.1095-8312.2010.01426.x}{10.1111/j.1095-8312.2010.01426.x}.

>>>>

6. Nieukerken EJ van, Kaila L, Kitching IJ, Kristensen NP, Lees DC, et
al. (2011) Order Lepidoptera. In: Animal biodiversity: an outline of
higher-level classification and survey of taxonomic richness. Zootaxa.
pp. 212--221.

@@

12. Ferrer-Paris JR, S\'anchez-Mercado A, Viloria \'AL, Donaldson J (2013)
Congruence and Diversity of Butterfly-Host Plant Associations at Higher
Taxonomic Levels. PloS one 8: e63570.
doi:\href{http://dx.doi.org/10.1371/journal.pone.0063570}{10.1371/journal.pone.0063570}.

@@

19. Kodandaramaiah U, Lees DC, M\"uller CJ, Torres E, Karanth KP, et al.
(2010) Phylogenetics and biogeography of a spectacular Old World
radiation of butterflies: the subtribe Mycalesina (Lepidoptera:
Nymphalidae: Satyrini). BMC Evol Biol 10: 172. 
doi:\href{http://dx.doi.org/10.1186/1471-2148-10-172}{10.1186/1471-2148-10-172}.

20. Kodandaramaiah U, Pe\~na C, Braby MF, Grund R, M\"uller CJ, et al.
(2010) Phylogenetics of Coenonymphina (Nymphalidae: Satyrinae) and the
problem of rooting rapid radiations. Mol Phylogenet Evol 54: 386--394.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2009.08.012}{10.1016/j.ympev.2009.08.012}.

21. Ortiz-Acevedo E, Willmott KR (2013) Molecular systematics of the
butterfly tribe Preponini (Nymphalidae: Charaxinae). Syst Entomol 38:
440--449.
doi:\href{http://dx.doi.org/10.1111/syen.12008}{10.1111/syen.12008}.

22. De-Silva DL, Day JJ, Elias M, Willmott KR, Whinnett A, et al. (2010)
Molecular phylogenetics of the Neotropical butterfly subtribe Oleriina
(Nymphalidae: Danainae: Ithomiini). Mol Phylogenet Evol 55: 1032--1041.
doi:\href{http://dx.doi.org/10.1016/j.ympev.2010.01.010}{10.1016/j.ympev.2010.01.010}.

@@

44. FitzJohn RG, Maddison WP, Otto SP (2009) Estimating trait-dependent
speciation and extinction rates from incompletely resolved phylogenies.
Syst Biol 58: 595--611. Available:
doi:\href{http://dx.doi.org/10.1093/sysbio/syp067}{10.1093/sysbio/syp067}.

@@

52. M\"uller CJ, Wahlberg N, Beheregaray LB (2010) `After Africa': the
evolutionary history and systematics of the genus Charaxes Ochsenheimer
(Lepidoptera: Nymphalidae) in the Indo-Pacific region. Biol J Linn Soc
100: 457--481.
doi:\href{http://dx.doi.org/10.1111/j.1095-8312.2010.01426.x}{10.1111/j.1095-8312.2010.01426.x}.
